### 2017-07-27 paper/oopsla17-cameraready/evaluation-user-study.tex
some Wes comments

We assigned three problems to the students: the |padZero| and
|mulByDigit| programs from \autoref{sec:qualitative}, as well as
the following |sepConcat| program
%
\begin{ecode}
  let rec sepConcat sep sl =
    match sl with
    | [] -> ""
    | h::t ->
        let f a x = a ^ (sep ^ x) in
        let base = (*@\hlTree{[]}@*) in
        (*@\hlSherrloc{List.fold\_left f base sl}@*)
\end{ecode}
%
where the student has erroneously returned the empty list, rather than
the empty string, in the base case of the fold.
% which triggers an error on line 7.
%
% For each problem the students were given the ill-typed program and
% either \ocaml's error or \toolname's jump-compressed trace;
%
The full user study is available in \autoref{sec:user-study-exams}.
%
Due to the nature of an in-class exam not every student answered every
question, but we always received at least 12 (out of a possible 15 or
16) responses for each problem-tool pair.
%
A further complication for this study is that this session of the course
was taught in \textsc{Reason}\footnote{\url{https://reasonml.github.io}},
a dialect of \ocaml with a more C-like syntax, and thus for the study
we transcribed the programs to \textsc{Reason} syntax.

@@

\paragraph{Conclusion.}
%
We collected exams from 31 students, though due to the nature of the
study not every student completed every problem.
%
The number of complete submissions was always at least 12 out of
a maximum of 15 or 16 per program-tool pair.
%
While our results are not statistically significant,
collecting more responses per test pair was not possible as it
would require having students answer the same problem twice (once with
\sherrloc and once with \toolname).

@@

\mypara{Results}
%
The measured kappa values were $\kappa = 0.68$ for the explanations and
$\kappa = 0.77$ for the fixes; while there is no formal notion for what
consititutes strong agreement~\cite{Krippendorff2012-wd}, kappa values
above $0.60$ are often called ``substantial''
agreement~\cite{Landis1977-ey}.
%
Figure~\ref{fig:results-user-study} summarizes a single annotator's
results, which show that students given \toolname's blame assignment
were generally more likely to correctly explain and fix the type error
than those given \sherrloc's.
%
While there was no discernible difference between \toolname and
\sherrloc for |sepConcat|, \toolname responses for |padZero| and
|mulByDigit| were marked correct 5--25\% more often than the \sherrloc
responses.
%
While the results appear to show a trend in favor of \toolname,
they do not rise to the level of statistical significance.
% The results appear to show a trend in favor of \toolname;
% %
% however, none rise to the level of statistical significance.
%

>>>>

We assigned three problems to the students: the |padZero| and
|mulByDigit| programs from \autoref{sec:qualitative}, as well as
the following |sepConcat| program
%
\begin{ecode}
  let rec sepConcat sep sl =
    match sl with
    | [] -> ""
    | h::t ->
        let f a x = a ^ (sep ^ x) in
        let base = (*@\hlTree{[]}@*) in
        (*@\hlSherrloc{List.fold\_left f base sl}@*)
\end{ecode}
%
where the student has erroneously returned the empty list, rather than
the empty string, in the base case of the fold.
% which triggers an error on line 7.
%
% For each problem the students were given the ill-typed program and
% either \ocaml's error or \toolname's jump-compressed trace;
%
The full user study is available in \autoref{sec:user-study-exams}.
%
Due to the nature of an in-class exam, not every student answered every
question, but we always received at least 12 (out of a possible 15 or
16) responses for each problem-tool pair.
%
%A further complication for this study is that
This session of the course
was taught in \textsc{Reason},\footnote{\url{https://reasonml.github.io}}
a dialect of \ocaml with a more C-like syntax, and thus for the study
we transcribed the programs to \textsc{Reason} syntax.

@@

\paragraph{Subjects.}
%
We collected exams from 31 students, though due to the nature of the
study not every student completed every problem.
%
The number of complete submissions was always at least 12 out of
a maximum of 15 or 16 per program-tool pair.
%
% While our results are not statistically significant,
% collecting more responses per test pair was not possible as it
% would require having students answer the same problem twice (once with
% \sherrloc and once with \toolname).

@@

\mypara{Results}
%
The measured kappa values were $\kappa = 0.68$ for the explanations and
$\kappa = 0.77$ for the fixes; while there is no formal notion for what
consititutes strong agreement~\cite{Krippendorff2012-wd}, kappa values
above $0.60$ are often called ``substantial''
agreement~\cite{Landis1977-ey}.
%
Figure~\ref{fig:results-user-study} summarizes a single annotator's
results, which show that students given \toolname's blame assignment
were generally more likely to correctly explain and fix the type error
than those given \sherrloc's.
%
There was no discernible difference between \toolname and
\sherrloc for |sepConcat|; however, \toolname responses for |padZero| and
|mulByDigit| were marked correct 5--25\% more often than the \sherrloc
responses.
%
While the results appear to show a trend in favor of \toolname,
they do not rise to the level of statistical significance;
further investigation is merited.
% The results appear to show a trend in favor of \toolname;
% %
% however, none rise to the level of statistical significance.
%
